\documentclass[11pt]{article}

% --- arXiv-friendly preamble (standard packages only) ---
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=1in]{geometry}
\usepackage{booktabs}
\usepackage{amsmath,amssymb}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{cleveref} % must load AFTER hyperref

\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\gstar}{G$^{*}$}

\title{\textbf{When Does a Code Graph Help a Coding Agent?}\\
\large Blast Radius, Model Capability, and Tool Altitude in Change-Impact Tasks}

\author{
  Tapabrata ``Topo'' Pal\\
  \texttt{topo.pal@gmail.com}
}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
A widespread intuition holds that giving an LLM coding agent a resolved code
graph (callers, callees, implementors, dispatch) makes it more effective on
existing code than plain text search (grep/ripgrep + read). In a controlled,
paired study that isolates the context mechanism and scores against independent
compiler-grade oracles---across two languages (Go, Java), three model tiers, and
change-impact tasks spanning 1--108 change-sites---we find the intuition is true
but \emph{doubly} conditional: on task size, and on the \emph{altitude} at which
the graph is exposed to the agent. (1)~On small, name-greppable changes the graph
ties text at every model tier. (2)~On large-blast-radius changes
($\approx$100 change-sites) the graph exposed as \emph{query primitives}
(look up a symbol, list callers, list implementors) acts as a capability
equalizer, lifting weaker models ($+0.17$ to $+0.24$ mean recall) and collapsing
the variance that makes text search silently incomplete---but orchestrating a
multi-turn traversal over primitives is itself a frontier-model skill, so the
smallest tier leaves much of the benefit unrealized (mean recall $0.833$ with the
same tools a frontier model drives to $1.000$). (3)~Exposing the \emph{same
graph} at \emph{task altitude}---a single deterministic
$\code{change\_impact}(\text{method})$ operation that computes the declaration,
the override/implementation family, and all resolved callers inside the
engine---removes the orchestration barrier entirely: every tier, including the
smallest, reaches mean recall $0.997$, and completeness becomes
\emph{tier-invariant}. The smallest model with the task-level operation
(\$0.11/task) outperforms the frontier model with text search (\$2.14/task) and
matches the frontier model driving graph primitives (\$3.06/task) at $1/28$th the
cost and $5$--$15\times$ fewer agent turns. Tier-invariance extends below the
commercial API floor: a local 30B model (zero API cost) achieves the same
$0.997$ mean recall in a single agent turn. The pattern replicates in a second
framework (Guava, a 310-site change): the small tier collapses on text
($0.17$) but sits at the engine ceiling ($0.997$) with the operation, at
$1/21$st the frontier-text cost. The engine operation itself scores
$0.993$ recall / $0.948$ precision against the oracle with no LLM in the loop.
Building the deterministic operation also surfaced five latent resolution defects
that every LLM-orchestrated arm had silently absorbed---evidence that
task-shaped operations are not only more effective but \emph{testable}. We give
the mechanism and the boundary it predicts, and argue that structural code tools
should ship task-shaped operations rather than primitive kits, and be evaluated
on completeness-and-consistency at fixed cost, conditioned on blast radius
\emph{and} interface altitude.
\end{abstract}

\paragraph{Honesty note.}
An earlier version of this study reported a \emph{negative} result (``code graphs
don't beat text search''). That conclusion was too broad: it was drawn from Go
tasks that were, in hindsight, almost all small and name-greppable. Extending the
study to a larger, polymorphism-heavy Java framework
(\code{jackson-databind})---with a precise type-resolution oracle and a
size-graded task set---surfaced the boundary the Go data had missed, and a
subsequent extension surfaced a second, independent condition: the interface
altitude at which the graph is offered. The honest result is \emph{conditional
twice over}: the graph's value is real but bounded to large-blast-radius
change-impact tasks, and \emph{who can realize it} is gated by whether the tool
demands orchestration the model cannot reliably supply. We report exactly where
it helps, where it does not, and the mechanism that predicts which is which.

\section{Introduction}
\label{sec:intro}

LLM coding agents work on existing code through a loop: \textbf{locate} relevant
code (search), \textbf{read} it, \textbf{traverse} structure (who calls / what
implements), and \textbf{stop} when subjectively confident. Two paradigms supply
the context: text search, and a resolved code graph. The graph holds strictly
more accurate structural information, so the natural hypothesis is that it
produces more complete, better-calibrated behavior on change-impact tasks, where
a missed call site is a broken build.

We set out to confirm this in Go and \emph{could not}---graph tied text on
completeness and calibration. The honest reading at the time was a negative
result. But our Go tasks, after outcome-blind auditing, were almost all
\emph{small} (1--22 change-sites) and \emph{name-greppable}. The question the Go
data could not answer was whether the graph earns its keep where text search
structurally struggles. We therefore extended the study to \code{jackson-databind},
a polymorphism- and reflection-heavy Java framework whose interface methods
(\code{JsonDeserializer.deserialize}, \code{JsonSerializer.serialize}, \ldots)
have dozens of implementations and call sites---and built a \emph{size-graded}
task set with a precise type-resolution oracle. That extension found the first
boundary: blast radius.

The blast-radius result, however, contained a puzzle. The graph's recall
advantage was largest exactly where the model was weakest---yet the weak model
still left much of the advantage on the table. With identical graph primitives,
the frontier tier reached recall $1.000$ and the small tier only $0.833$. The
graph had the answer; the small model could not extract it. This motivated a
second extension: move the extraction \emph{into the tool}. We implemented the
change-impact traversal as a single deterministic operation inside the graph
engine---$\code{change\_impact}(\text{method}) \rightarrow$ declaration $+$
override/implementation family $+$ resolved callers---and re-ran the grid with a
third arm that exposes only this operation. The result is the second boundary:
\emph{tool altitude}. At task altitude, completeness is tier-invariant
($0.997$ at every tier), and the cheapest model becomes the best-value system in
the study.

\paragraph{Contributions.}
\begin{enumerate}[leftmargin=*]
\item \textbf{A methodology that isolates the tool across two languages}---identical
tasks, enforced tool allowlists per arm, scored against \emph{independent}
oracles (Go \code{go-ssa-vta}; a new Java Spoon oracle that resolves every call
site by type, not by name).
\item \textbf{The size-conditioned result}: graph $\approx$ text on
small/greppable change-impact tasks; graph $\gg$ text on large-blast-radius
tasks, on recall \emph{and} variance. The discriminator is blast radius
(specifically, change-sites reachable only via caller edges), \emph{not} name
ambiguity and not language.
\item \textbf{A capability-conditioned reading}: with graph \emph{primitives},
the recall lift shrinks as the model strengthens---the graph is a quality lever
for weak/mid models and a cost lever at the frontier.
\item \textbf{The tool-altitude result (new)}: the same graph exposed as a single
task-level \code{change\_impact} operation makes completeness tier-invariant
(mean recall $0.997$ at every tier). The smallest model then outperforms the
frontier model on text search at $1/20$th the cost, and matches the frontier
model on graph primitives at $1/28$th. Orchestration over primitives, not graph
access, was the binding constraint.
\item \textbf{A testability finding}: implementing the traversal as a
deterministic, oracle-scorable engine operation exposed five latent Java
resolution defects (multi-line signatures, generic bounds parsed as inheritance,
wildcard-import scope, same-file shadowing over typed receivers, nested generic
types) that every LLM-orchestrated arm had silently absorbed. Task-shaped
operations are not only more effective; they are \emph{debuggable}.
\item \textbf{Reproducible artifacts}: a Java change-impact oracle and
size-graded task generator, a scoring fix (line$\rightarrow$method
normalization) without which graph arms are silently under-credited, and the
graph-native \code{change\_impact} operation itself.
\end{enumerate}

\section{Related work}
\label{sec:related}

\paragraph{Agentic coding and repository-level evaluation.}
Benchmarks such as SWE-bench~\cite{swebench} and repository-level completion
suites~\cite{repobench,repocoder} established that resolving real changes requires
\emph{repository} context, not just local context. Agent scaffolds---SWE-agent's
agent--computer interface~\cite{sweagent}, and pipeline approaches such as
Agentless~\cite{agentless}---differ chiefly in \emph{how} they gather that
context. SWE-agent demonstrated that interface design materially changes agent
performance at fixed model; our tool-altitude result quantifies one axis of that
design space for structural code tools: the same underlying capability, offered
as primitives versus as a task-shaped operation, produces a $0.16$ mean-recall
swing for a small model. Our study isolates the context mechanism directly,
rather than as part of an end-to-end agent.

\paragraph{Code context: retrieval vs.\ structure.}
Retrieval-augmented generation~\cite{rag} and its code-specific
variants~\cite{repocoder} supply context by similarity; code-graph approaches
supply it by resolved structure. Graph-based code context for
LLMs~\cite{codexgraph} and graph-structured retrieval more
broadly~\cite{graphrag} argue structure should help. We ask the prior question
empirically---\emph{when} does the structure change the answer rather than just
the path to it---and find the answer is conditioned on task size, model
capability, and interface altitude.

\paragraph{Static call-graph construction (our oracle, not the tool under test).}
Sound change-impact ground truth requires resolved dispatch. We use Class
Hierarchy Analysis~\cite{cha} and Variable Type Analysis~\cite{vta} lineage call
graphs (Go \code{go-ssa-vta}) and, for Java, source-level type resolution via
Spoon~\cite{spoon} (cf.\ bytecode frameworks Soot~\cite{soot} and
WALA~\cite{wala}). Crucially the oracle is \emph{independent} of the graph tool
under test, so we never grade the tool against itself.

\section{A variable framework for agent code-context}
\label{sec:framework}

Three cost axes---\textbf{tokens, latency, round-trips, setup}; six quality
axes---\textbf{completeness, precision, calibration, consistency, freshness,
determinism}; one outcome---\textbf{task success}; one
meta-variable---\textbf{cost-of-error}. To these we add a tool-design
axis this study shows is load-bearing: \textbf{interface altitude}---whether the
tool exposes \emph{primitives} the agent must orchestrate (look up, list callers,
list implementors) or a \emph{task-shaped operation} that returns the completed
traversal. Our prior belief was that the graph's value lived in the quality axes
uniformly. The result below is that it lives in \textbf{completeness +
consistency, past a task-size threshold}, and that \emph{who can collect it}
depends on altitude: at primitive altitude the payoff is gated by model
capability; at task altitude it is not.

\section{Study design}
\label{sec:design}

\paragraph{Arms (only the tool description/allowlist differs).}
\textbf{T} text (rg/grep/read); \textbf{G} graph primitives (typed \code{prism}
call-graph CLI---symbol lookup, references, typed edge traversal---plus rg for
anchor discovery); \textbf{V} text-primary with graph-as-verifier; and, in the
altitude extension, \textbf{\gstar{}} task-level graph (the agent may call
\code{prism change-impact 'Type.method(Params)'}, which returns declaration,
override/implementation family, and resolved callers in one response, plus rg
and symbol search for identifying the target). Arm enforcement is by
\code{--allowedTools} with a recorded \code{tool\_trace}; runs where the G arm
never touched the graph---or the \gstar{} arm never called
\code{change-impact}---are flagged (\code{violation}) and excluded.

\paragraph{Mode A (context quality).}
The agent answers ``list every site that must change to do X,'' declaring
\code{complete} + \code{unresolved}. This isolates the tool from patch-writing
skill. (Mode B / compile-and-test is future work, \cref{sec:threats}.)

\paragraph{Independent oracles---never the graph under test.}
\emph{Go:} the \code{go-ssa-vta} call graph (via \code{grove-eval}) and/or the
merged-PR diff (codegen/mocks filtered). \emph{Java:} a Spoon type-resolution
oracle. Given a target method, it emits the declaration + the full
override/implementation family + every call site whose executable \emph{resolves}
(by type, not by name) into that family. This is the discipline a bare-name
oracle lacks: a call to an unrelated same-named method on a different type is
excluded. On jackson it resolved all $\sim$500 \code{get}/\code{set} call sites
and kept only the 3--22 that are truly jackson's (0 unresolved). Ground truth is
human-spot-checked and, where text reaches it, validated by a text arm hitting
recall 1.0. The oracle and the graph engine under test are \emph{separate
implementations} (a compiler frontend versus a tree-sitter-based incremental
indexer); their agreement is the measurement, and---as \cref{sec:bugs}
shows---their disagreement was the debugging signal.

\paragraph{A scoring pitfall (Java).}
\code{prism} reports authoritative \code{file:line}, so graph-arm agents naturally
answer sites as \code{File.java:114} rather than \code{File.java:method}. A
name-based scorer matches those at 0, silently penalizing the \emph{graph} arm
(e.g.\ a 148-site correct answer scored 0.0). We build a Spoon
line$\rightarrow$method index and normalize numeric answers to their innermost
enclosing method before scoring. All Java numbers below are post-normalization.
We flag this because it is an easy way to accidentally under-report a structural
tool's performance.

\paragraph{Subjects and size grading.}
Go: 14 tasks, 1--93 sites (localization controls, greppable enumeration controls,
change-impact). Java: \code{jackson-databind} @ 2.18.8, 6 interface-method
signature-change tasks spanning \textbf{8, 22, 38, 58, 104, 108} change-sites,
chosen to trace a size curve and to vary name-ambiguity independently of size.
\textbf{Models:} a small, a mid, and a frontier tier (denoted Haiku / Sonnet /
Opus).

\paragraph{Two experiments.}
\emph{Experiment 1} (T vs.\ G vs.\ V; $n{=}5$ trials per cell; 157 scored runs)
establishes the blast-radius and capability results
(\cref{sec:results-exp1}). \emph{Experiment 2} (the altitude extension;
\cref{sec:altitude}) adds the \gstar{} arm across all three tiers and all six
Java tasks, with fresh T and G baselines re-run on the repaired engine
(next paragraph); $\approx$50 additional scored runs. The \gstar{} engine
operation is deterministic, so per-cell variance in \gstar{} can arise only from
the agent's query formulation and answer relay; we replicate the small tier
($n{=}3$) and observe the determinism directly (\cref{sec:altitude}).

\paragraph{Engine repair between experiments (a result in itself).}
Implementing \code{change\_impact} \emph{inside} the graph engine---and scoring
its raw output against the independent oracle with no LLM in the loop---exposed
five latent Java resolution defects in the engine's indexer that Experiment~1's
LLM-driven G arm had partially masked by supplementing the graph with its own
reading (\cref{sec:bugs}). All five were fixed with regression tests before
Experiment~2; Experiment~2's G baselines therefore run on a strictly better
engine than Experiment~1's, which biases \emph{against} the altitude effect we
report (the primitives arm is as strong as we can make it). Text arms are
unaffected by engine version.

\section{Results I: blast radius and capability (graph as primitives)}
\label{sec:results-exp1}

\subsection{Small / greppable change-impact: graph $\approx$ text}
Across the Go tasks, mean recall(G) $\approx$ recall(T) (within $\sim$0.01--0.07
every task; no consistent direction). Greppable controls reach recall $\approx$1.0
for every arm. The small Java tasks behave identically: \code{jsonnode-get} (8
sites) and \code{settable-set} (22 sites) tie ($\Delta$recall $\le 0.01$) on the
small model---\emph{despite} being the most name-ambiguous targets in the set
(grep over-match $64\times$ and $18\times$). Ambiguity did not help the graph.

\subsection{The size curve}
\label{sec:curve}
\Cref{tab:curve} gives the full size-graded curve (recall, $n=5$,
post-normalization). The small model ran the 4 original tasks; the mid and
frontier models ran all 6.

\begin{table}[ht]
\centering
\small
\begin{tabular}{lrccccc}
\toprule
task & sites & Small T & Small G & Mid T & Mid G & Frontier T \(\to\) G \\
\midrule
jsonnode-get      & 8   & 0.97 & 0.97 & 0.78 & \textbf{0.93} & 0.93 \(\to\) 0.95 \\
settable-set      & 22  & 0.90 & 0.91 & 0.93 & 0.97          & 0.97 \(\to\) 0.99 \\
writeTypePrefix   & 38  & ---  & ---  & 0.97 & 1.00          & 1.00 \(\to\) 1.00 \\
serializeWithType & 58  & ---  & ---  & 0.99 & 1.00          & 0.99 \(\to\) 1.00 \\
deserialize       & 104 & 0.52 & \textbf{0.69} & 0.76 & \textbf{0.93} & 0.92 \(\to\) \textbf{0.96} \\
serialize         & 108 & 0.62 & \textbf{0.85} & 0.86 & \textbf{1.00} & 1.00 \(\to\) 1.00 \\
\bottomrule
\end{tabular}
\caption{Experiment 1: recall across three model tiers and the jackson size
curve, graph exposed as primitives. The graph's recall advantage is largest for
the weakest model on the largest tasks, shrinks as the model strengthens, and is
$\le 0.04$ everywhere at the frontier.}
\label{tab:curve}
\end{table}

The robust, large signal is at the \textbf{large tasks (104/108): graph $+0.13$ to
$+0.24$, on both the small and mid tiers.} The \textbf{mid-size dispatch tasks
(38/58) tie on recall}---the mid model's text arm maxes out (0.97--0.99) because
their change-sets are small and the call sites are name-matched. And the advantage
is \emph{not} explained by grep ambiguity, which runs opposite to the effect (the
most ambiguous targets are the smallest).

\paragraph{The one small-task exception is mechanistically informative.}
On \code{jsonnode-get} (8 sites) the mid model's \emph{text} arm drops to 0.78,
and the graph recovers it ($+0.15$). The sites text consistently missed are
\code{JsonNode.has}, \code{JsonNode.hasNonNull}, and \code{ArrayNode.\_at}---methods
that \emph{call} \code{get(int)} but whose own names do \emph{not} contain
``get.'' A grep-for-\code{get} agent finds the get-named declarations and call
lines but misses \emph{callers named after something else}; the graph's caller
edges return them directly. So the true predictor is not raw size but
\textbf{the number of change-sites reachable only via caller edges, not by the
target's name}---which grows with blast radius (the large tasks have many such
indirect callers) but can bite even a tiny task. This is the sharpest single
illustration of the mechanism.

\subsection{The gain survives a stronger model, then converts at the frontier}
\label{sec:tiers}
A natural objection: a stronger model brute-forces the large enumeration with text
and closes the gap. Going small$\rightarrow$mid, text \emph{did} improve
(serialize $0.62\rightarrow0.87$)---but the graph improved more
($0.85\rightarrow0.996$) and stayed ahead on \emph{both} large tasks
(\cref{tab:tiers}). At the frontier the advantage is conditioned on task
difficulty: on \code{serialize} the frontier text arm fully enumerates the change
(1.00, 24 turns) and the graph is redundant; but on the harder \code{deserialize},
even frontier text drops sites (mean 0.923, one run at \textbf{0.71}) while the
graph holds 0.962---higher recall, lower variance (sd .05 vs .12), \emph{and}
cheaper (\$4.69 vs \$5.64/run). The recall advantage shrinks monotonically with
capability but \emph{does not vanish on hard tasks}---it converts into a
reliability + cost edge.

\begin{table}[ht]
\centering
\small
\begin{tabular}{lcc}
\toprule
tier & serialize (108) & deserialize (104, \emph{harder}) \\
\midrule
Small    & $.62 \to .85$ (\textbf{+.24}) & $.52 \to .69$ (\textbf{+.17}) \\
Mid      & $.87 \to 1.00$ (\textbf{+.13}) & $.76 \to .94$ (\textbf{+.17}) \\
Frontier & $1.00 \to 1.00$ (+.00)         & $.92 \to \mathbf{.96}$ (\textbf{+.04}) \\
\bottomrule
\end{tabular}
\caption{Experiment 1: recall (text $\to$ graph, $\Delta=$ G$-$T) on the two
large tasks across tiers. With primitives the graph is a capability equalizer:
large lift for weak models, narrowing to a hard-task reliability/cost edge at the
frontier. Note the equalization is \emph{partial}---the small tier's graph arm
(.69/.85) remains far below the frontier's (.96/1.00) with identical tools.}
\label{tab:tiers}
\end{table}

\subsection{The graph removes catastrophic misses (a consistency gain)}
\label{sec:consistency}
The tier data show more than a higher mean: the \emph{variance} differs. Mid-model
text on \code{serialize} swings from 1.00 to 0.73 across nominally identical
runs---it silently misses $\sim$30\% of sites on some trials. The graph is
$0.996 \pm {\sim}0$: \emph{zero catastrophic runs}. On a change task, where one
missed site is a broken build, this reliability is arguably more valuable than the
mean lift. This is the completeness/calibration benefit the single-tier Go study
looked for and could not find; it emerges only once tasks are large enough that
text \emph{can} fail, and it persists to the frontier on hard tasks (frontier text
dipped to 0.71 on \code{deserialize}; the graph stayed at 0.96).

\subsection{Cost: cheaper in the middle, par at the top, overhead tax at the bottom}
\label{sec:cost}
Cost (USD/run) depends on the regime. On the \textbf{large tasks} (mid tier) the
graph buys $+0.13$--$0.17$ recall for $\sim$10\% more (G/T $\approx$ 1.07--1.16):
``better answer, $\sim$same price''---text cannot reach the graph's recall at
\emph{any} reasonable budget. On the \textbf{mid-size tasks} recall ties but the
graph is $\sim$25--37\% \emph{cheaper} (G/T $\approx$ 0.63--0.77), recovering a
token-efficiency result at matched quality. On the \textbf{small tasks} per-call
overhead makes the graph pricier (G/T $\approx$ 1.24--1.28) where text was already
near-complete. \textbf{At the frontier the graph becomes a cost lever}: recall
ties on all six tasks but the graph is cheaper on 4 of 6, including every mid/large
task (G/T $\approx$ 0.64--0.90), undercutting a frontier model grinding 24--39 text
turns.

\subsection{Calibration}
In aggregate over small tasks, over-confidence is tied (both arms assert
\code{complete} at $\sim$0.9 recall on \code{settable-set}: 5/5 each)---the Go
negative holds there. The graph's calibration benefit is specifically the variance
collapse on large tasks (\cref{sec:consistency}), not a uniform over-confidence
reduction.

\section{Results II: tool altitude (graph as a task-level operation)}
\label{sec:altitude}

Experiment 1 leaves a gap between what the graph \emph{knows} and what a weak
model can \emph{extract from it}: with identical primitives, the small tier
plateaus at mean recall $0.833$ while the frontier tier reaches $1.000$.
Experiment 2 closes the gap by moving the extraction into the engine. The
\gstar{} arm may issue one command---%
\code{prism change-impact 'Type.method(Params)'}---whose response is the
completed traversal: the declaration, every override/implementation in the
subtype closure, and every call site whose receiver \emph{resolves} into that
family. The agent's residual job is to identify the target method from the issue
text, run the command, and relay the result.

\subsection{Completeness becomes tier-invariant}
\Cref{tab:altitude} gives recall for all three arms at all three tiers on the six
Java tasks (repaired engine; one fresh trial per cell, small-tier \gstar{}
replicated $n{=}3$).

\begin{table}[ht]
\centering
\small
\setlength{\tabcolsep}{4.5pt}
\begin{tabular}{lrccccccccc}
\toprule
& & \multicolumn{3}{c}{Small} & \multicolumn{3}{c}{Mid} & \multicolumn{3}{c}{Frontier} \\
\cmidrule(lr){3-5}\cmidrule(lr){6-8}\cmidrule(lr){9-11}
task & sites & T & G & \gstar{} & T & G & \gstar{} & T & G & \gstar{} \\
\midrule
jsonnode-get      & 8   & 1.00 & 1.00 & \textbf{1.00} & 1.00 & 1.00 & \textbf{1.00} & 1.00 & 1.00 & \textbf{1.00} \\
settable-set      & 22  & 0.91 & 1.00 & \textbf{1.00} & 0.95 & 0.95 & \textbf{1.00} & 1.00 & 1.00 & \textbf{1.00} \\
writeTypePrefix   & 38  & 0.84 & 1.00 & \textbf{1.00} & 1.00 & 1.00 & \textbf{1.00} & 1.00 & 1.00 & \textbf{1.00} \\
serializeWithType & 58  & 0.60 & 0.60 & \textbf{1.00} & 1.00 & 1.00 & \textbf{1.00} & 1.00 & 1.00 & \textbf{1.00} \\
deserialize       & 104 & 0.43 & 0.67 & \textbf{1.00} & 0.75 & 0.93 & \textbf{1.00} & 0.71 & 1.00 & \textbf{1.00} \\
serialize         & 108 & 0.76 & 0.72 & \textbf{0.98} & 1.00 & 0.98 & \textbf{0.98} & 1.00 & 1.00 & \textbf{0.98} \\
\midrule
\textbf{mean}     &     & 0.76 & 0.83 & \textbf{1.00} & 0.95 & 0.98 & \textbf{1.00} & 0.95 & 1.00 & \textbf{1.00} \\
\bottomrule
\end{tabular}
\caption{Experiment 2: recall by arm and tier on the repaired engine (means to
two decimals; exact \gstar{} mean 0.997 at every tier). Under \gstar{},
completeness is tier-invariant---the per-task values are \emph{identical} across
tiers, including the one shared miss (serialize 0.98, an engine residual, not a
model failure). The small tier's remaining T/G deficits vanish entirely.}
\label{tab:altitude}
\end{table}

Three observations. \textbf{First, the \gstar{} column is the same at every
tier}: per-task recall is identical to three decimals, and the single shared
imperfection (serialize $0.982$) traces to two call sites the engine's
chained-receiver inference cannot yet resolve (\code{w.serializer.serialize})---an
engine residual, visible and fixable in one place, rather than a stochastic model
failure distributed over a transcript. \textbf{Second, the small tier gains the
most}: mean recall moves from $0.758$ (T) and $0.833$ (G) to $0.997$
(\gstar{})---the entire equalization Experiment 1 promised but could not deliver
through primitives. \textbf{Third, the frontier gains too}: not in recall (Opus~G
already reached $1.000$) but in effort---4 agent turns instead of 21, 70 seconds
instead of 429 (\cref{tab:altcost}).

The determinism is visible in the transcripts. The small model's entire tool use
on the 8-site task is one line---%
\code{prism change-impact 'JsonNode.get(int)' .}---followed by the relayed
answer: 2 turns, 22.6 seconds, \$0.04, recall 1.0. The small-tier replication
($n{=}3$ per task, 18 runs) scored \emph{identically} in every trial: per-task
recall and precision are exact across trials, as the deterministic engine
output predicts. Site sets were byte-identical in four of six tasks; in the
other two, a single trial transcribed one method's directory path differently
while naming the same method---relay noise, not a traversal difference, and
scored identically. The residual stochastic surface (query formulation)
produced no failures.

\subsection{The economics invert}
\label{sec:alt-econ}

\begin{table}[ht]
\centering
\small
\begin{tabular}{llrrr}
\toprule
tier & arm & mean recall & \$/task & agent turns \\
\midrule
Small    & T        & 0.758 & 0.48 & 31 \\
Small    & G        & 0.833 & 0.53 & 41 \\
Small    & \gstar{} & \textbf{0.997} & \textbf{0.11} & \textbf{2.8} \\
\addlinespace
Mid      & T        & 0.951 & 2.13 & 45 \\
Mid      & G        & 0.978 & 2.20 & 44 \\
Mid      & \gstar{} & \textbf{0.997} & \textbf{0.53} & \textbf{11.7} \\
\addlinespace
Frontier & T        & 0.952 & 2.14 & 22 \\
Frontier & G        & 1.000 & 3.06 & 21 \\
Frontier & \gstar{} & 0.997 & \textbf{0.48} & \textbf{4.0} \\
\addlinespace
Local 30B & \gstar{} & \textbf{0.997} & \textbf{free} & \textbf{1.0} \\
\bottomrule
\end{tabular}
\caption{Experiment 2: mean recall, cost, and agent turns over the six Java
tasks. The small model at task altitude (\$0.11/task) outperforms the frontier
model on text (\$2.14) and matches the frontier on primitives (\$3.06) at
$1/28$th the cost. Local 30B (qwen3-coder:30b, Ollama, no API cost) matches
all commercial tiers at task altitude and completes each task in a single turn.}
\label{tab:altcost}
\end{table}

At primitive altitude, completeness must be \emph{bought with model capability}:
the recall ladder ($0.833 \to 0.978 \to 1.000$) tracks the price ladder
(\$0.53 $\to$ \$2.20 $\to$ \$3.06). At task altitude the ladder collapses: every
tier delivers $0.997$, so the rational choice is the cheapest tier, and the
cost of a near-complete change-set falls from \$3.06 (frontier + primitives) to
\$0.11 (small + \gstar{})---a $28\times$ reduction at a $-0.003$ recall
difference. Against the strongest text baseline (frontier T, $0.952$ mean with a
$0.71$ dip on \code{deserialize}), the small + \gstar{} system is
\emph{strictly better}: higher mean, no tail risk, $1/20$th the cost, $5\times$
fewer turns. Once the traversal lives in the engine, the completeness of a
change-set is a property of the \emph{tool}, and the model reverts to what it is
actually needed for: identifying the target and consuming the result.

\subsection{The engine ceiling, measured without an LLM}
\label{sec:ceiling}
Because the \gstar{} operation is deterministic, we can score it directly against
the oracle with no model in the loop: mean recall $0.993$, mean precision
$0.948$ across the six tasks (per-task recall $\ge 0.974$; the misses are three
call sites behind chained receivers and one multi-line call-site argument-count
extraction). Agent-mediated \gstar{} runs reproduce this ceiling ($0.997$; the
small difference reflects task-scope judgments such as including supertype
declarations). This decomposition---engine ceiling measured deterministically,
agent overhead measured separately---is only possible \emph{because} the
traversal is a tool, and we propose it as the right way to evaluate structural
code tools: report the tool's oracle score and the agent's realization of it,
not a single conflated number. Precision at task altitude is high but not
perfect ($0.80$ on the overload-ambiguous 8-site task, where callers of other
\code{get} overloads are included absent literal-argument evidence;
$0.97$--$1.00$ elsewhere).

\subsection{What building the operation revealed: LLM arms absorb engine defects}
\label{sec:bugs}
The deterministic operation initially scored recall \emph{0.05} on the 108-site
task. Tracing every oracle miss to a mechanism exposed five latent defects in the
engine's Java resolution---(1) signatures truncated at the first line, so
wrapped \code{extends}/\code{implements} clauses and annotations destroyed
inheritance edges; (2) generic bounds (\code{<T extends Enum<T>{}>}) parsed as
inheritance; (3) wildcard imports resolving to nothing; (4) same-file method
shadowing defeating explicitly-typed receivers; (5) nested generics breaking
field-type inference. All five were fixed with regression tests; recall rose
$0.05 \to 0.99$ from engine fixes alone.

The methodological point: \emph{these defects were invisible in Experiment 1}.
The G arm's LLM supplemented the degraded graph with its own reading and grep,
producing plausible mid-range recall (0.6--0.9) that read as ``the graph helps
somewhat'' rather than ``the graph is broken.'' An LLM in the loop is an adaptive
error-masker: it converts tool defects into quiet score depression. A
deterministic, oracle-scored operation converts them into visible, traceable,
fixable failures. This is an argument for task-shaped tools independent of the
performance argument: they make the structural layer of an agent system
\emph{testable}.

\subsection{Mode B: recall deficit as expected compile failures}
\label{sec:modeb}
Recall is a continuous metric, but the downstream consequence of a missed site
in a signature-change task is discrete: every override or call site not
returned by the agent is a method still using the old signature---a compile
error when the change is applied. The expected compile failures for a run is
therefore exactly $(1 - \text{recall}) \times |GT|$, and the question ``does the
completeness win matter?'' has a binary answer at the task level.

\begin{table}[ht]
\centering
\small
\begin{tabular}{lrrrrc}
\toprule
system & \multicolumn{4}{c}{missed sites per task} & broken? \\
\cmidrule(lr){2-5}
 & 8 & 22--58 & 104 & 108 & (tasks) \\
\midrule
Opus+T      & 0 & 0     & \textbf{30} & 0           & 1/6 \\
Sonnet+T    & 0 & 0     & \textbf{26} & 0           & 1/6 \\
Haiku+T     & 0 & 2--23 & \textbf{59} & \textbf{26} & 5/6 \\
\addlinespace
Haiku+\gstar{}     & 0 & 0 & 0 & 2 & 1/6 \\
Sonnet+\gstar{}    & 0 & 0 & 0 & 2 & 1/6 \\
Opus+\gstar{}      & 0 & 0 & 0 & 2 & 1/6 \\
Local 30B+\gstar{} & 0 & 0 & 0 & 2 & 1/6 \\
\bottomrule
\end{tabular}
\caption{Mode B: missed sites = expected compile errors if the agent's answer
were applied. On the 104-site task every text arm leaves 26--59 methods broken;
every \gstar{} tier leaves 0. The 2-site miss on the 108-site task is
the chained-receiver engine ceiling, shared identically by all \gstar{} tiers.}
\label{tab:modeb}
\end{table}

On the 104-site task the gap is not statistical: Opus+T at \$2.63/run leaves
30 methods with the old signature; every \gstar{} tier at any cost (including
free) leaves none. For 5/6 tasks all \gstar{} configurations produce
zero-miss answers---guaranteed compile-clean on those tasks. The remaining
2-site miss on the 108-site task is the engine-ceiling residual (three call
sites behind chained receivers); it affects all \gstar{} tiers identically,
confirming it is a tool property, not a model property.

\subsection{External validity: Apache Commons Collections}
\label{sec:external}

To test whether the patterns in \cref{tab:altitude} are specific to
\code{jackson-databind}, we generated two boundary-case tasks in Apache
Commons Collections 4: a small greppable change
(\code{Transformer.transform}, 17 sites) and a large cross-hierarchy change
(\code{MapIterator.next}, 142 oracle sites).

\textbf{The small-task tie replicates.} On \code{Transformer.transform}
every arm---Sonnet+T, Sonnet+\gstar{}, and local 30B+\gstar{}---achieves
recall $1.0$, confirming the small-task tie is not specific to
\code{jackson-databind}. The efficiency asymmetry persists even at equal
recall: the T arm needed 61 agent turns (512\,s); \gstar{} needed 27
(185\,s), and the local arm one call.

\textbf{The large task failed audit and is excluded.} \code{MapIterator}
extends \code{java.util.Iterator}, which invalidates the task on three
independent grounds. First, the refactor is ill-posed:
\code{MapIterator.next()} \emph{overrides} \code{Iterator.next()}, so its
signature cannot change without breaking the JDK contract---``every site
that must change'' has no coherent answer. Second, the oracle's ground
truth for such a target is a virtual-dispatch closure through the external
interface: it includes call sites whose receiver is a plain
\code{java.util.Iterator} (e.g.\ \code{CollectionUtils.addAll}), which
would not change under any reading of the task. Third, \code{next} is
generic enough that the scorer's symbol-only fallback dominates---55 of the
83 credited sites per arm were weak matches, and the T and \gstar{} arms
received identical scores for near-identical answer sets, i.e.\ the number
measures the matcher, not the search strategy. We exclude the task under
the same audit discipline that discarded the bare-name commons-lang tasks
(\cref{sec:threats}).

The attempt still produced a mechanism finding: the graph engine's family
traversal stopped at external supertypes (project-local recall on the
dispatch closure: $0.32$), even though the \code{extends} clause that roots
the hierarchy is \emph{in project source}. In response the engine now (a)
reports a contract boundary (\code{completeness: project-local} +
\code{overridesExternal}) whenever the queried method belongs to an external
supertype's contract---the excluded task above now \emph{self-reports} its
ill-posedness---and (b) answers external-rooted queries
(\code{Iterator.next}) with the project-local implementation closure, the
well-posed migration form of the question. The task generator likewise
rejects targets that override external methods.

\textbf{Large-task replication: Guava, 310 sites.} The audit constrained
the replacement target: large, rooted in a \emph{project-local} type,
distinctively named. \code{ForwardingObject\#delegate} in Guava qualifies
(310 oracle sites: 84-member override family + 280 resolved callers; three
times the largest jackson task). The engine ceiling on it is $0.997$ recall
at $1.000$ precision.

\begin{table}[ht]
\centering
\small
\begin{tabular}{llrrrrr}
\toprule
tier & arm & recall & prec & turns & wall (s) & USD \\
\midrule
Haiku  & T        & 0.171 & 1.000 & 41 & 173 & 0.43 \\
Haiku  & \gstar{} & \textbf{0.997} & 1.000 & 4 & 102 & 0.18 \\
Sonnet & T        & 0.997 & 1.000 & 55 & 811 & 3.85 \\
Sonnet & \gstar{} & 0.961 & 0.909 & 25 & 314 & 1.75 \\
Opus   & T        & 0.997 & 1.000 & 3 & 516 & 5.46 \\
Opus   & \gstar{} & \textbf{0.997} & 1.000 & 8 & 119 & 0.66 \\
Fable  & \gstar{} & \textbf{0.997} & 1.000 & 9 & 155 & 1.40 \\
Local 30B & \gstar{} & \textbf{0.997} & 1.000 & \textbf{1} & 224 & \textbf{0} \\
\bottomrule
\end{tabular}
\caption{Guava \code{ForwardingObject.delegate} (310 sites), one trial per
cell. A first Haiku~T attempt exhausted a 20-minute budget without
answering; the scored run is a 40-minute-budget retry that answered early
and incompletely (54 sites), claiming completeness.}
\label{tab:guava}
\end{table}

Three findings. \emph{First}, ceiling delivery replicates: Haiku~\gstar{},
Opus~\gstar{}, Fable~\gstar{}, and the local 30B all sit exactly at the
engine ceiling ($0.997$) on a blast radius $3\times$ anything in the
jackson corpus, while Haiku~T collapses to $0.171$ (or times out)---the
capability-equalizer result, reproduced in a third corpus at $1/21$st the
frontier-text cost. \emph{Second}, Sonnet~T and Opus~T \emph{tie} recall
here. \code{delegate()} is a globally unique, literally greppable name, so
the change-set---though huge---never exceeds what text search reliably
enumerates. This sharpens the boundary variable: the graph's recall
advantage is gated by \emph{text-enumerability}, not raw site count
(jackson's \code{serialize} callers required type-level disambiguation
among same-named methods; \code{delegate()} does not). The economics still
invert at equal recall: \$3.85--\$5.46 and up to 55 turns versus \$0 and
one turn. \emph{Third}, a new mechanism datum: Sonnet~\gstar{} scored
\emph{below} every other \gstar{} tier ($0.961$, precision $0.909$)
because it re-processed the engine's output through its own
grep/awk/python pipeline across 25 turns, dropping 12 real sites and
adding 30 spurious ones, then asserted completeness. The scaffolded local
arm and the Haiku/Opus/Fable arms relayed the deterministic set
losslessly (the Fable run touched no tool but \code{prism}). Relay
fidelity is thus not a capability gradient but a \emph{behavioral}
variable---any tier can fumble it by re-deriving. At task altitude the
model's remaining job is relay; capability spent re-orchestrating a
solved traversal is negative capability. The product implication: ship
the relay discipline (a steering rule that forbids re-deriving the
tool's answer---now part of the shipped templates), not just the tool.

\subsection{Cross-language external validity: Go and TypeScript}
\label{sec:crosslang}

The same protocol extends beyond Java. In each language the engine
ceiling is measured first (no LLM), then the arms.

\textbf{Go (grafana, \code{SQLStore.WithTransactionalDbSession}, 93
sites).} Resolving this target required one engine fix (Go receiver
methods live in any file of the type's package; the contains edge
previously required same-file declarations), after which the ceiling is
$1.000$ recall / $1.000$ precision. The historical text/primitives arms
from Experiment~1 average $0.817$ (T) and $0.826$ (G) at the small tier,
with per-trial recall swinging $0.495$--$1.0$. At task altitude:
Haiku~\gstar{} $1.000/1.000$ in 5 turns (75\,s, \$0.10); local
30B~\gstar{} $1.000/1.000$ in one turn (81\,s, \$0). The variance
collapse is total. The two other large grafana targets root in an
\emph{external} plugin-SDK interface, the Go analog of the excluded
commons-collections task---Go's structural typing leaves no
\code{implements} clause to traverse, so nominal closure cannot answer
them (engine roadmap: method-set matching).

\textbf{TypeScript (TypeORM, \code{Driver.escape}, 37 sites,
compiler-resolved GT via a ts-morph oracle).} The engine ceiling is
\emph{low}: $0.540$ recall / $0.645$ precision. Family resolution works
(11 of 12 driver implementations; \code{implements Driver} clauses are
nominal), but callers bind through interface-typed \emph{fields}
(\code{this.driver.escape(...)}) in files that never import a concrete
driver, and the TS call resolver does not yet track field types. The
local 30B \gstar{} arm scores exactly the ceiling ($0.540/0.645$, one
turn)---a lossless relay of an imperfect engine, and the cleanest
demonstration in the study that \gstar{} completeness is a tool
property: raise the ceiling and every tier rises; here the ceiling is
low and every relay lands on it. Text arms can exceed a low ceiling
(the boundary cuts both ways), which is precisely what the
per-language ceiling measurement is for.

\section{Why---the mechanism}
\label{sec:mechanism}

A change to a method's signature forces every declaration/override \emph{and}
every call site to change. Three regimes:
\begin{itemize}[leftmargin=*]
\item \textbf{Few sites, statically named (Go, small Java).} A call
\code{x.Foo(...)} and an implementor \code{func (T) Foo(...)} both contain
\code{Foo}; with $\le\!\sim$20 sites a capable agent greps the name, reads to
confirm, and enumerates them all. The graph's structural precision saves reading
effort (a token wash) but rarely changes \emph{what it finds}. Hence the tie.
\item \textbf{Many sites, graph as primitives (Java framework interfaces,
$\sim$100).} Now grep+read is a manual graph traversal at scale, and so---
crucially---is \emph{driving the graph primitives}. The agent must choose seeds,
chain lookup$\to$references$\to$overrides$\to$callers per family member, hold
$\sim$100 partial results across 30--60 turns, and union them without loss. Each
step is individually easy; their conjunction is a long-horizon orchestration task
whose success probability decays with length and with model capability. This is
why the primitives arm equalizes only partially: the graph removes the
\emph{search} burden but leaves the \emph{orchestration} burden, and
orchestration is itself a frontier skill.
\item \textbf{Many sites, graph at task altitude.} The traversal is one
deterministic closure computed where the data lives. The LLM's remaining surface
is target identification and relay---short-horizon, low-variance work that every
tier performs equally well. Completeness stops being a model property and
becomes a tool property; the tiers converge.
\end{itemize}

This predicts the boundary structure we observe: the graph earns its keep
wherever the change-set exceeds what text search reliably enumerates; \emph{who}
collects that value depends on whether the tool's interface demands
orchestration; and at task altitude the value is collected by construction. Name
ambiguity is a red herring at every altitude: a capable agent disambiguates
\code{get}/\code{set} by reading, as long as there are few sites to check.

\section{Discussion}
\label{sec:discussion}
\begin{itemize}[leftmargin=*]
\item \textbf{Ship task-shaped operations, not primitive kits.} The largest gains
in this study came not from adding structure but from moving a traversal across
the tool boundary. For agent tool builders (MCP servers, IDE integrations), the
design rule is: identify the traversals agents repeatedly orchestrate---%
change-impact, dead-code reachability, test-coverage closure---and expose each as
one deterministic operation returning the completed answer. Primitives remain
useful for ad-hoc exploration; they are the wrong \emph{primary} interface for
completeness-critical tasks.
\item \textbf{The economics of completeness invert.} At primitive altitude,
completeness is purchased with model capability (the recall ladder tracks the
price ladder). At task altitude the cheapest model matches the frontier, so the
marginal dollar should go to the engine, not the model. This bears directly on
deployment: a \$0.11 small-model configuration strictly dominated a \$2.14
frontier-text configuration in our study. Local open-weights models become
\emph{fully equivalent} carriers of frontier-grade change-impact analysis: a
30B model (qwen3-coder:30b, Ollama) running at task altitude scores 0.997
mean recall across the six Java tasks---identical to Haiku, Sonnet, and
Opus---at zero API cost and in a single agent turn. The same model fails
entirely on primitives (multi-turn orchestration collapses). The tier
invariance at task altitude therefore extends below the commercial API floor.
\item \textbf{Evaluate context tools conditioned on blast radius and altitude.}
``Graphs help'' and ``graphs don't'' are both wrong, and so is any comparison
that fixes the interface silently. The honest figure of merit is
completeness-and-consistency at fixed cost, as a function of \#change-sites,
with the tool's oracle ceiling and the agent's realization of it reported
separately (\cref{sec:ceiling}).
\item \textbf{Deterministic operations make agent systems testable.} The
five-defect arc (\cref{sec:bugs}) generalizes: any capability buried in an LLM
orchestration loop is shielded from regression testing by the model's adaptive
error-masking. Moving it into a scorable tool is how it becomes engineering.
\item \textbf{Language matters only through task size.} Java surfaced the effect
not because Java is ``harder to grep'' but because framework interface methods
produce 100-site change-sets that Go application code in our sample rarely did.
The prediction is testable in large Go codebases with wide interfaces.
\end{itemize}

\section{Threats to validity}
\label{sec:threats}
\begin{itemize}[leftmargin=*]
\item \textbf{Experiment 2 trial counts.} \gstar{} cells run $n{=}3$ (small
tier) and $n{=}1$ (mid, frontier); T/G baselines in \cref{tab:altitude} are
single fresh trials on the repaired engine (Experiment 1 supplies $n{=}5$
history for T/G on the older engine, consistent in direction). The engine's
output is deterministic and independently scored (\cref{sec:ceiling}), so
\gstar{} variance is confined to query formulation; the small-tier replication
observed no score variance (two trials differed from their siblings only in
the transcribed directory of one site each). Larger $n$ on the remaining cells
is cheap and planned.
\item \textbf{Query formulation is prompt-assisted.} Our task prompts name the
changing method (as a signature-change ticket would); \gstar{} still requires the
agent to produce the parameter-typed query. Tasks where the target must first be
\emph{localized} from a vague report exercise a skill \gstar{} does not
address---there T/G localization ability still binds.
\item \textbf{Oracle--engine independence.} The oracle (Spoon, compiler-grade)
and the engine (tree-sitter indexer + resolution heuristics) both perform type
resolution but share no code or algorithms; the engine's initial 0.05 recall and
residual 0.993 (not 1.0) demonstrate they do not trivially agree.
\item \textbf{Corpus coverage.} The altitude results now span three Java
frameworks: jackson-databind (6 size-graded tasks), Apache Commons
Collections (small-task tie; one large-task attempt failed audit---the
target overrode a JDK interface, making the refactor ill-posed, the oracle
closure over-broad, and the generic name scorer-hostile---and is excluded;
such targets are now rejected at task-generation time), and Guava (310-site
replication, \cref{tab:guava}, $n{=}1$ per cell). A large Go codebase with
wide interfaces remains untested, and the Guava cells warrant replication
trials.
\item \textbf{Mode A only.} We score the \emph{answer}, not an applied patch. Mode
B (compile / fail-to-pass)---where an incomplete change actually breaks the
build---would test whether the reliability gain converts to task success.
\item \textbf{One graph implementation} and a soft tool gate (arms can decline
their tools; we exclude violating runs, but the offer-vs-enforce distinction is
unmodeled).
\item \textbf{Construct / selection.} Java ground truth is type-resolved (no
bare-name pollution); an earlier bare-name Java attempt was discarded after audit.
Go ground-truth pollution and codegen churn were mitigated after discovery; earlier
positive readings on hand-picked tasks did not survive outcome-blind sampling.
\item \textbf{Determinism.} Recall/precision come from the oracle scorers and cost
from per-run accounting; no LLM is in the measurement loop, so the numbers are
reproducible from the released run logs.
\end{itemize}

\section{Conclusion}
\label{sec:conclusion}
The intuition that a resolved code graph makes an agent more complete on
change-impact tasks is \emph{conditionally true, and the conditions are blast
radius and tool altitude}. On small, name-greppable changes the graph ties text
at every model tier. On large-blast-radius changes, the graph as
\emph{primitives} is a partial capability equalizer: it lifts weaker models and
collapses variance, but orchestrating it remains a frontier skill, so the
weakest models leave most of the benefit unrealized. The same graph exposed as a
single deterministic \code{change\_impact} operation completes the
equalization: recall becomes tier-invariant ($0.997$), the smallest model
strictly dominates the frontier-model text baseline at $1/20$th the cost, and
the completeness of a change-set becomes a testable property of the tool rather
than an emergent property of the model. The earlier blanket negative was an
artifact of a small-task sample; the blanket positive (``graphs obviously
help'') is equally wrong; and the primitives-only framing under-sells the graph
exactly where it matters most. The defensible, mechanistic claim: \textbf{a code
graph pays off in proportion to how far a change exceeds what text search
reliably enumerates---and that payoff reaches whichever models the tool's
interface altitude permits. At task altitude, it reaches all of them.}

\section*{Artifact availability}
\label{sec:artifacts}
The graph engine (Grove, including the \code{change\_impact} operation), the
agent-facing context CLI/MCP server (Prism, exposing
\code{prism\_change\_impact}), and the evaluation harness (arms runner, tasks,
the Spoon change-impact oracle, the line$\rightarrow$method rescorer, and the
recall/cost aggregators) are open source. All analyses are reproducible
\emph{without} an LLM from the released run logs via the deterministic scorers.
\begin{itemize}[leftmargin=*]
\item Grove (code-intelligence graph + \code{change-impact} op): \url{https://github.com/provasign/grove}
\item Prism (agent context CLI / MCP server): \url{https://github.com/provasign/prism}
\item Evaluation harness, Java oracle, and task definitions: \url{https://github.com/provasign/research}
\end{itemize}

% ---------------------------------------------------------------------------
% ---------------------------------------------------------------------------
\begin{thebibliography}{99}
\small

\bibitem{swebench} C.~E. Jimenez, J.~Yang, A.~Wettig, S.~Yao, K.~Pei, O.~Press,
and K.~Narasimhan. SWE-bench: Can Language Models Resolve Real-World GitHub
Issues? \emph{ICLR}, 2024.

\bibitem{sweagent} J.~Yang, C.~E. Jimenez, A.~Wettig, K.~Lieret, S.~Yao,
K.~Narasimhan, and O.~Press. SWE-agent: Agent-Computer Interfaces Enable Automated
Software Engineering. \emph{NeurIPS}, 2024.

\bibitem{agentless} C.~S. Xia, Y.~Deng, S.~Dunn, and L.~Zhang. Agentless:
Demystifying LLM-based Software Engineering Agents. \emph{arXiv:2407.01489}, 2024.

\bibitem{repobench} T.~Liu, C.~Xu, and J.~McAuley. RepoBench: Benchmarking
Repository-Level Code Auto-Completion Systems. \emph{ICLR}, 2024.

\bibitem{repocoder} F.~Zhang, B.~Chen, Y.~Zhang, J.~Keung, J.~Liu, D.~Zan,
Y.~Mao, J.-G. Lou, and W.~Chen. RepoCoder: Repository-Level Code Completion
Through Iterative Retrieval and Generation. \emph{EMNLP}, 2023.

\bibitem{rag} P.~Lewis et al. Retrieval-Augmented Generation for
Knowledge-Intensive NLP Tasks. \emph{NeurIPS}, 2020.

\bibitem{codexgraph} X.~Liu et al. CodexGraph: Bridging Large Language Models and
Code Repositories via Code Graph Databases. \emph{arXiv:2408.03910}, 2024.

\bibitem{graphrag} D.~Edge et al. From Local to Global: A Graph RAG Approach to
Query-Focused Summarization. \emph{arXiv:2404.16130}, 2024.

\bibitem{cha} J.~Dean, D.~Grove, and C.~Chambers. Optimization of Object-Oriented
Programs Using Static Class Hierarchy Analysis. \emph{ECOOP}, 1995.

\bibitem{vta} V.~Sundaresan, L.~Hendren, C.~Razafimahefa, R.~Vall\'ee-Rai,
P.~Lam, E.~Gagnon, and C.~Godin. Practical Virtual Method Call Resolution for
Java. \emph{OOPSLA}, 2000.

\bibitem{spoon} R.~Pawlak, M.~Monperrus, N.~Petitprez, C.~Noguera, and
L.~Seinturier. Spoon: A Library for Implementing Analyses and Transformations of
Java Source Code. \emph{Software: Practice and Experience}, 46(9):1155--1179, 2016.

\bibitem{soot} R.~Vall\'ee-Rai, P.~Co, E.~Gagnon, L.~Hendren, P.~Lam, and
V.~Sundaresan. Soot---a Java Bytecode Optimization Framework. \emph{CASCON}, 1999.

\bibitem{wala} IBM. T.J. Watson Libraries for Analysis (WALA).
\url{https://github.com/wala/WALA}.

\end{thebibliography}

\end{document}
